---
title: '`r params[["title"]]`'
author:
- name: '`r params[["author_name"]]`'
  affiliation: '`r params[["author_affiliation"]]`'
  email: '`r params[["author_email"]]`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
monofont: 'Source Code Pro'
monofontoptions: 'Scale=0.7'
params:
  output_directory: "/EPIC_QC"
  csv_file: "sample_sheet_clean.csv"
  data_directory: "/idats"
  array: "EPIC"
  annotation: "ilm10b4.hg19"
  filter_snps: TRUE
  filter_non_cpg: TRUE
  filter_xy: TRUE
  filter_multihit: TRUE
  filter_beads: TRUE
  population: NULL
  bead_cutoff: 0.05
  detection_pvalues: 0.01
  filter_callrate: TRUE
  callrate_samples: 0.99
  callrate_probes: 1
  gender_threshold: -2 
  gender_colname: NULL
  norm_background: "oob"
  norm_dye: "RELIC"
  norm_quantile: "quantile1" 
  cell_tissue: NULL
  pca_vars: !r c("Sample_Plate", "Sentrix_ID")
  title: "EPIC Array Quality-Control"
  author_name: "Firstname Lastname"
  author_affiliation: "Institution"
  author_email: "some@email.com"
  cache: FALSE
  show_code: FALSE
  n_cores: 20
  dpi: 120
  gg_fontsize: 12
output:
  bookdown::html_document2:
    theme: simplex
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
    fig_width: 6.3
    fig_height: 4.7
    number_sections: true
    self_contained: true
    mathjax: default
    df_print: kable
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
options(stringsAsFactors = FALSE)

output_directory <- params[["output_directory"]]

if (params[["cache"]]) {
  dir.create(paste0(output_directory, "/cache/"), recursive = TRUE, showWarnings = FALSE, mode = "0777")
}


### Load packages and functions
library(parallel)
library(tidyverse)
library(scales)
library(grid)

### Set knitr rmarkdown chunk options
knitr::opts_chunk$set(
  results = "asis",
  size = "small",
  include = TRUE,
  echo = params[["show_code"]],
  warning = params[["show_code"]],
  message = params[["show_code"]],
  dpi = params[["dpi"]],
  tidy = FALSE,
  crop = TRUE,
  autodep = TRUE,
  fig.align = "center",
  fig.pos = "!H",
  cache = params[["cache"]],
  cache.path = paste0(output_directory, "/cache/"),
  fig.path = paste0(output_directory, "/cache/")
)


### Define n_cores
n_cores <- params[["n_cores"]]


### Define theme
ggplot2::theme_set(ggplot2::theme_light(base_size = params[["gg_fontsize"]]))


### Additional packages and functions
pretty_kable <- function(
  data, 
  font_size = 12, 
  format_args = list(scientific = -1, digits = 3, big.mark = ","), 
  col.names = NA,
  full_width = NULL,
  echo = TRUE,
  ...
) {
  colnames(data) <- Hmisc::capitalize(colnames(data))
  options(knitr.table.format = "html")
  output <- knitr::kable(x = data, format.args = format_args, col.names = col.names, ...)
  output <- kableExtra::kable_styling(
    kable_input = output,
    bootstrap_options = c("striped", "hover", "condensed", "responsive"),
    full_width = ifelse(is.null(full_width), FALSE, full_width),
    position = "center",
    font_size = font_size
  )
  
  if (echo) print(output) else invisible(output)
}

do_check_gender <- !is.null(params[["gender_colname"]])
do_cell_composition <- !is.null(params[["cell_tissue"]])
```

# Methods

1. Importing Data
    * __File format__  
        => IDAT files from Illumina
    * __Import data__  
        => (custom) `read_idats` based on [*minfi*](https://doi.org/doi:10.18129/B9.bioc.minfi)
1. Filtering Probes
    * `filter_snps` ([Zhou et al., 2016](https://www.doi.org/10.1093/nar/gkw967))  
        => should probes in which the probed CpG falls near a SNP be removed?
    * `filter_non_cpg`  
        => should non-cg probes be removed?
    * `filter_xy`  
        => should probes from X and Y chromosomes be removed?

1. Filtering Probes
    * `filter_multihit` ([Nordlund et al., 2013](https://www.doi.org/10.1186/gb-2013-14-9-r105))  
        => should probes which align to multiple locations be removed?
    * `filter_beads`  
        => should probes with a beadcount less than 3 be removed (for at least 5 % of the samples)?
    * __Call Rate__  
        => should probes with less than the specified call rate (`r params[["callrate_probes"]]`) for detection p-values below $\alpha=`r params[["detection_pvalues"]]`$ be removed?
1. Filtering Samples
    * __Call Rate__  
        => should samples with less than the specified call rate (`r params[["callrate_samples"]]`) for detection p-values below $\alpha=`r params[["detection_pvalues"]]`$ be removed?
    * __Gender~[Phenotype]~ $\neq$ Gender~[Probes]~__  
        => flag samples with gender discrepancy
1. Normalisation
    * __Probe design type bias__  
        => using `rcp` method from [*ENmix*](https://doi.org/doi:10.18129/B9.bioc.ENmix)  
        *`rcp` = "Regression on Correlated Probes"*  
        *Normalise __type II__ probes (with __type I__ as reference) using linear regression coefficients based on type I and type II probe pairs within specified distance*
    * __Batch effect bias__  
        => using `ComBat` method from [*sva*](https://doi.org/doi:10.18129/B9.bioc.sva)  
        *Empirical Bayes framework is used to correct for batch effects using __batch/slide__ as covarariate*
1. Additional Checks
    * __Cell Composition__  
        => using `RefFreeCellMix` method from [*RefFreeEWAS*](https://cran.r-project.org/package=RefFreeEWAS)  
    * __Principal Component Analysis (PCA)__  
        => using [FlashPCA](https://doi.org/10.1093/bioinformatics/btx299) for R on [GitHub](https://github.com/gabraham/flashpca/tree/master/flashpcaR)


# Parameters

* Array: `r params[["array"]]`
* Annotation package from bioconductor: `r params[["annotation"]]`
* `filter_snps`: `r params[["filter_snps"]]`
* `filter_non_cpg`: `r params[["filter_non_cpg"]]`
* `filter_xy`: `r params[["filter_xy"]]`
* `filter_multihit`: `r params[["filter_multihit"]]`
* `filter_beads`: `r params[["filter_beads"]]`
* Name of the ethnicity population: `r params[["population"]]`
* The threshold for beadcount: `r params[["bead_cutoff"]]`
* The threshold for the detection pvalues: `r params[["detection_pvalues"]]`
* `filter_callrate`: `r params[["filter_callrate"]]`
* The call rate threshold for samples: `r params[["callrate_samples"]]`
* The call rate threshold for probes: `r params[["callrate_probes"]]`
* The threshold value to discrimate gender: `r params[["gender_threshold"]]`
* The method to estimate background normal distribution parameters: `r params[["norm_background"]]`
* The dye bias correction: `r params[["norm_dye"]]`
* The quantile normalisation: `r params[["norm_quantile"]]`
* The cell tissue: `r params[["cell_tissue"]]`


# Quality Control

```{r sample_sheet}
sample_sheet <- readr::read_csv(params[["csv_file"]])  %>% 
  dplyr::mutate(
    gender_clean = if (do_check_gender) {
      c("1" = 1, "2" = 2, "M" = 1, "F" = 2, "0" = 2)[get(params[["gender_colname"]])]
    } else {
      NULL
    }
  ) %>% 
  dplyr::select(Sample_ID, dplyr::everything())

readr::write_csv(x = sample_sheet, path = paste0(tempdir(), "/sample_sheet.csv"))

if (do_check_gender) {
  pca_vars <- intersect(colnames(sample_sheet), unique(c(params[["pca_vars"]], "gender_clean")))
} else {
  pca_vars <- intersect(colnames(sample_sheet), params[["pca_vars"]])
}
```

```{r read_idats}
output <- utils::capture.output({
  data_mset <- CARoT::read_idats(
    directory = params[["data_directory"]], 
    csv_file = paste0(tempdir(), "/sample_sheet.csv"), 
    meth_value_type = "B",
    filter_beads = params[["filter_beads"]], 
    bead_cutoff = params[["bead_cutoff"]], 
    filter_non_cpg = params[["filter_non_cpg"]],
    filter_snps = params[["filter_snps"]], 
    population = params[["population"]], 
    filter_multihit = params[["filter_multihit"]],
    filter_xy = FALSE, 
    detection_pvalues = params[["detection_pvalues"]],
    filter_callrate = params[["filter_callrate"]],
    callrate_samples = params[["callrate_samples"]],
    callrate_probes = params[["callrate_probes"]],
    norm_background = params[["norm_background"]],
    norm_dye = params[["norm_dye"]],
    norm_quantile = params[["norm_quantile"]],
    array_name = params[["array"]], 
    annotation_version = params[["annotation"]],
    n_cores = params[["n_cores"]]
  )
}, type = "message")
output <- output[grep(pattern = "[CARoT] Filtering IDAT files ...", output, fixed = TRUE):length(output)]
output <- output[!grepl(pattern = "^[=[]", x = output)]
cat(output, sep = "\n\n")
phenotypes <- data_mset@metadata[["phenotypes"]]
```

```{r call_rate}
data_call_rate_samples <- phenotypes  %>% 
  as.data.frame() %>% 
	dplyr::select(Sample_ID, call_rate) %>% 
	dplyr::arrange(call_rate) %>% 
	dplyr::mutate(
		x = seq_along(call_rate),
		label = ifelse(call_rate < params[["callrate_samples"]], Sample_ID, NA)
	)
```
  
```{r call_rate_samples_tab}
tab_call_rate_samples <- lapply(phenotypes[["call_rate"]], `<`, c(0.90, 0.95, 0.97, 0.98, 0.99, 1)) %>% 
	do.call("rbind", .) %>%
	colSums() %>%
	data.frame(
		"Call Rate Threshold" = paste0("<", c("0.90", "0.95", "0.97", "0.98", "0.99", "1.00")),
		"Samples (N)" = .,
		"Samples (%)" = signif((. / nrow(data_call_rate_samples)) * 100, digits = 3),
		check.names = FALSE
	)
pretty_kable(tab_call_rate_samples)
```

```{r call_rate_samples_fig}
ggplot2::ggplot(
  data = data_call_rate_samples,
  mapping = ggplot2::aes(x = x, y = call_rate, label = label)
) +
  ggplot2::geom_point(
    colour = scales::viridis_pal()(1), 
    shape = 21,
    na.rm = TRUE
  ) +
  ggplot2::geom_hline(
    mapping = ggplot2::aes(yintercept = params[["callrate_samples"]]),
    colour = "black", 
    linetype = 2,
    na.rm = TRUE
  ) +
  ggrepel::geom_label_repel(
    # nudge_x = 200, 
    # nudge_y = 0.01,
    min.segment.length = ggplot2::unit(0, "lines"), 
    size = 2, 
    segment.colour = "black",
    colour = "black",
    na.rm = TRUE
  ) +
  ggplot2::labs(x = "Samples", y = "Call Rate") +
  ggplot2::scale_y_continuous(label = scales::percent) +
	ggplot2::scale_x_continuous(label = scales::comma)
```

## Cell composition

```{r do_cell_composition}
if (!do_cell_composition) {
  cat("No cell tissue was provided.\n")
}
```

```{r cell_composition, eval = do_cell_composition}
cell_comp <- switch(
  EXPR = params[["cell_tissue"]],
  "Blood" = {
    out <- FlowSorted.Blood.EPIC::estimateCellCounts2(
      rgSet = data_mset, 
      compositeCellType = "Blood",
      processMethod = "preprocessQuantile", 
      # probeSelect = cell_probes,
      # cellTypes = cell_types,
      referencePlatform = paste0('IlluminaHumanMethylation', params[["array"]]),
      referenceset = NULL, 
      IDOLOptimizedCpGs = NULL, 
      returnAll = FALSE,
      meanPlot = TRUE, 
      verbose = FALSE
    )$counts
    colnames(out) <- paste0("CellT_", colnames(out))
    out
  }, 
  "Chord" = {
    cat("No method defined yet")
  },
  {
    estimate_k_cluster <- function(Rmat, max_k = 25, n_cores = 1) {
      cluster <- parallel::makeCluster(n_cores)
      doParallel::registerDoParallel(cluster)

      svdRmat <- RefFreeEWAS::svdSafe(Rmat)
      tmp <- do.call("rbind", lapply(
        X = 0:max_k,
        mc_Rmat = Rmat,
        mc_svdRmat = svdRmat,
        FUN = function(Ktest, mc_Rmat, mc_svdRmat) {
          N1 <- dim(mc_Rmat)[1]
          N2 <- dim(mc_Rmat)[2]
          if (Ktest == 0) {
            tmpRminLU <- mc_Rmat
          } else {
            tmpRminLU <- mc_Rmat - mc_svdRmat$u[, 1:Ktest] %*% (mc_svdRmat$d[1:Ktest] * t(mc_svdRmat$v[, 1:Ktest]))
          }
          tmpSigSq <- rowSums(tmpRminLU * tmpRminLU) / N2
    
          c(
            K = Ktest,
            AIC =  2 * (N1 + Ktest * (N1 + N2)) + 
              N1 * N2 +
              N2 * sum(log(tmpSigSq)),
            BIC = log(N2) * (N1 + Ktest * (N1 + N2)) + 
              N1 * N2 + 
              N2 * sum(log(tmpSigSq))
          )
      }))

      parallel::stopCluster(cluster)

      list(
        icTable = tmp, 
        best = tmp[c(AIC = which.min(tmp[, "AIC"]), BIC = which.min(tmp[, "BIC"])), "K"],
        custom_best = tmp[c(
          AIC = which.max(abs(diff(tmp[, "AIC"])[-1])) + 1, 
          BIC = which.max(abs(diff(tmp[, "BIC"])[-1])) + 1
        ), "K"]
      )
    }
    beta_matrix <- minfi::getBeta(data_mset)
    max_k <- min(ncol(beta_matrix), 25)
    k_estimated <- min(estimate_k_cluster(
      Rmat = beta_matrix, 
      max_k = max_k, 
      n_cores = min(params[["n_cores"]], max_k)
    )$best)
    mu0 <- RefFreeEWAS::RefFreeCellMixInitialize(
      Y = beta_matrix,
      K = k_estimated,
      Y.Distance = NULL, 
      Y.Cluster = NULL, 
      largeOK = TRUE,
      dist.method = "euclidean"
    )
    
    RefFreeCellMixObj <- RefFreeEWAS::RefFreeCellMix(
      Y = beta_matrix, 
      mu0 = mu0, 
      K = NULL,
      iters = 10, 
      Yfinal = NULL, 
      verbose = FALSE
    )

    out <- RefFreeCellMixObj[["Omega"]]
    colnames(out) <- paste0("CellT_", 1:ncol(out))
    out
  }
)

phenotypes <- phenotypes %>% 
  as.data.frame() %>%
  dplyr::mutate(Sample_ID = as.character(Sample_ID)) %>% 
  dplyr::left_join(
    y = cell_comp %>% 
      as.data.frame() %>% 
      tibble::rownames_to_column("Sample_ID"), 
    by = "Sample_ID"
  ) %>% 
  S4Vectors::DataFrame()
```

```{r cell_composition_size}
def_res <- params[["dpi"]]
def_label_gene_y <- params[["gg_fontsize"]] / 8
def_label_gene_x <- params[["gg_fontsize"]] / 8

def_grid_h_middle <- 0.90
def_height <- nrow(sample_sheet) * 
  (def_label_gene_y * params[["gg_fontsize"]] / 0.75) / 
  def_grid_h_middle /
  def_res

def_height <- ifelse(def_height>=16, 16, def_height)
```

```{r cell_composition_fig, fig.height = def_height, eval = do_cell_composition}
CARoT::ggheatmap(
  data = phenotypes %>% 
    as.data.frame() %>% 
    dplyr::select(Sample_ID, dplyr::starts_with("CellT_")) %>% 
    tibble::column_to_rownames(var = "Sample_ID") %>% 
    tidyr::drop_na(), 
  dendrogram_columns = TRUE,
  dendrogram_rows = TRUE,
  line_size = 0.5,
  font_size = params[["gg_fontsize"]],
  font_size_x = def_label_gene_x,
  font_size_y = def_label_gene_y,
  distance_method = "euclidean",
  cluster_method = "ward.D2",
  scale_name = "Cell Composition",
  scale_revert = FALSE
)
```

## Gender check

```{r do_check_gender}
if (!do_check_gender) {
  cat("No phenotypes for gender was provided.\n")
}
```

```{r gender_check, eval = do_check_gender}
sex_predicted <- minfi::getSex(minfi::mapToGenome(data_mset), cutoff = params[["gender_threshold"]])
gender_density <- stats::density(sex_predicted$yMed - sex_predicted$xMed, n = 100000)
gender_threshold <- round(x = gender_density$x[which(diff(sign(diff(gender_density$y)))==2)], digits = 3)

phenotypes <- phenotypes %>% 
  as.data.frame() %>% 
  dplyr::mutate(Sample_ID = as.character(Sample_ID)) %>% 
  dplyr::left_join(
    y = data_mset %>% 
      minfi::mapToGenome() %>% 
      minfi::getSex(cutoff = gender_threshold) %>% 
      as.data.frame() %>% 
      dplyr::mutate(Sample_ID = minfi::sampleNames(data_mset)) %>% 
      dplyr::rename(
        qc_xmedian = xMed,
        qc_ymedian = yMed,
        qc_predicted_gender = predictedSex
      ), 
    by = c("Sample_ID")
  ) %>% 
  dplyr::mutate(
    qc_predicted_gender = c("1" = 1, "2" = 2, "M" = 1, "F" = 2, "0" = 2)[qc_predicted_gender],
    qc_observed_gender = gender_clean,
    qc_gender_discrepancy = qc_observed_gender!=qc_predicted_gender
  ) %>% 
  S4Vectors::DataFrame()
```

```{r gender_check_threshold, eval = FALSE}
ggplot2::ggplot(
  data = phenotypes %>%
    as.data.frame() %>%
    dplyr::mutate(diff = qc_ymedian - qc_xmedian),
  mapping = ggplot2::aes(x = diff)
) +
  ggplot2::geom_density(position = "identity", na.rm = TRUE) +
  ggplot2::geom_vline(xintercept = gender_threshold, linetype = 2, na.rm = TRUE) +
  ggplot2::labs(
    x = expression(atop(
      paste("Y chromosome median total intensity ", (log[2])),
      paste("- X chromosome median total intensity ", (log[2]))
    )),
    y = "Density"
  ) +
  ggplot2::scale_x_continuous(expand = ggplot2::expand_scale(mult = c(0, 0))) +
  ggplot2::scale_y_continuous(expand = ggplot2::expand_scale(mult = c(0, 0.05)))
```

```{r gender_check_fig, eval = do_check_gender}
ggplot2::ggplot(
  data = phenotypes %>% 
    as.data.frame() %>% 
    dplyr::filter(!qc_gender_discrepancy), 
  mapping = ggplot2::aes(
    x = qc_xmedian, 
    y = qc_ymedian, 
    shape = factor(qc_predicted_gender), 
    colour = factor(qc_observed_gender)
  )
) +
  ggplot2::geom_abline(
    data = data.frame(Threshold = paste("=", gender_threshold), Seuil = gender_threshold), 
    mapping = ggplot2::aes(intercept = Seuil, slope = 1, linetype = Threshold),
    na.rm = TRUE
  ) +
  ggplot2::geom_point(size = 2, na.rm = TRUE) +
  ggplot2::geom_point(
    data = phenotypes %>% 
      as.data.frame() %>% 
      dplyr::filter(qc_gender_discrepancy),
    size = 4,
    show.legend = FALSE,
    na.rm = TRUE
  ) +
  ggrepel::geom_label_repel(
    data = phenotypes %>% 
      as.data.frame() %>% 
      dplyr::filter(qc_gender_discrepancy),
    mapping = ggplot2::aes(x = qc_xmedian, y = qc_ymedian, label = Sample_ID),
    segment.colour = "black",
    colour = "black",
    min.segment.length = ggplot2::unit(0, "lines"),
    size = 2,
    inherit.aes = FALSE,
    show.legend = FALSE,
    na.rm = TRUE
  ) +
  ggplot2::labs(
    x = expression(atop("X chromosome", paste("Median total intensity ", (log[2])))), 
    y = expression(atop("Y chromosome", paste("Median total intensity ", (log[2]))))
  ) +
  ggplot2::scale_colour_viridis_d(
    name = "Gender (Observed)", 
    breaks = c(1, 2), 
    labels = c("Male", "Female"),
    drop = FALSE,
    begin = 0.2, 
    end = 0.8
  ) +
  ggplot2::scale_shape_manual(
    name = "Gender (Predicted)", 
    breaks = c(1, 2), 
    labels = c("Male", "Female"), 
    values = c(22, 21),
    drop = FALSE
  )
```

```{r descrepancy_table, eval = do_check_gender}
phenotypes %>%
  as.data.frame() %>% 
  group_by(qc_predicted_gender, qc_observed_gender) %>% 
  summarise(n = n()) %>% 
  ungroup() %>% 
  mutate(
    qc_observed_gender = paste("Observed:", qc_observed_gender),
    qc_predicted_gender = paste("Predicted:", qc_predicted_gender)
  ) %>% 
  spread(key = "qc_observed_gender", value = "n") %>% 
  rename(qc_predicted_gender = "") %>% 
  replace(list = is.na(.), values = 0) %>% 
  pretty_kable(full_width = FALSE)
```

```{r descrepancy_samples_table, eval = do_check_gender}
phenotypes %>% 
  as.data.frame() %>% 
  dplyr::filter(qc_gender_discrepancy) %>% 
  dplyr::select(Sample_Name, Sample_ID, qc_observed_gender, qc_predicted_gender) %>% 
  pretty_kable(full_width = FALSE)
```

```{r filter_xy, eval = params[["filter_xy"]]}
switch(
  EXPR = params[["array"]],
  "450k" = utils::data("probe.features", package = "ChAMPdata"),
  "EPIC" = utils::data("probe.features.epic", package = "ChAMPdata")
)
probe_features <- get("probe.features")
autosomes <- probe_features[!probe_features$CHR %in% c("X", "Y"), ]
mset_f2 <- data_mset[minfi::featureNames(data_mset) %in% rownames(autosomes), ]
cat(
  "Filtering probes on the X or Y chromosome:\n\n",
  "  - ", scales::comma(dim(data_mset)[1] - dim(mset_f2)[1]), " probes were discarded"
)
data_mset <- mset_f2
```

## Principal Component Analysis

```{r normalisation, results = "hide"}
norm_beta <- ENmix::rcp(mdat = data_mset)
if (length(unique(minfi::pData(data_mset)[["Sentrix_ID"]])) > 1) { 
  norm_beta <- ENmix::ComBat.mc(
    dat = norm_beta, 
    batch = factor(minfi::pData(data_mset)[["Sentrix_ID"]]), 
    nCores = params[["n_cores"]], 
    mod = NULL
  )
}
colnames(norm_beta) <- minfi::pData(data_mset)[["Sample_ID"]]
if (min(norm_beta, na.rm = TRUE) <= 0) {
  norm_beta[norm_beta <= 0] <- min(norm_beta[norm_beta > 0])
}
if (max(norm_beta, na.rm = TRUE) >= 1) {
  norm_beta[norm_beta >= 1] <- max(norm_beta[norm_beta < 1])
}
data_mset@metadata[grep("_values", names(data_mset@metadata))] <- NULL
data_mset@metadata[["norm_beta_values"]] <- norm_beta
```

```{r export}
data_mset@metadata[["phenotypes"]] <- phenotypes
readr::write_rds(x = data_mset, path = paste0(output_directory, "/", params[["array"]], "_mset.rds"))
```

```{r pca}
list_beta <- c(
	"raw_beta" = "Raw $beta$-values",
	"norm_beta" = "ComBat normalised $beta$-values"
)
data_batch <- list(
	"raw_beta" =  minfi::getBeta(data_mset) %>% 
	  `colnames<-`(minfi::pData(data_mset)[, "Sample_ID"]),
	"norm_beta" = data_mset@metadata[["norm_beta_values"]]
)

for (ibeta in seq_along(list_beta)) {
	cat("\n###", list_beta[ibeta], " {.tabset .tabset-fade .tabset-pills}\n\n")
	CARoT::pca_report(
		data = data_batch[[names(list_beta)[ibeta]]], 
		design = data_mset@metadata[["phenotypes"]], 
		id_var = "Sample_ID",
		technical_vars = pca_vars, 
		n_comp = min(10, ncol(data_batch[[names(list_beta)[ibeta]]])), 
		fig_n_comp = min(3, ncol(data_batch[[names(list_beta)[ibeta]]])),
		title_level = 4
	)
	cat("\n")
}
```

# R session information

```{r session_info, results = "markup"}
options("width" = 110)
sessioninfo::session_info()
```
